MSDS_6372_Project2

### 2022-07-25 MSDS_6372_Project2.Rmd
commit objective 1 draft

# Other useful libraries
library(dplyr)
library(ggplot2)

@@

#####################################################################################
#                                       Loess plots                                 #
#####################################################################################
```{r, Loess plot}
bonemed_df$fracture.num<-ifelse(bonemed_df$fracture=="Yes",1,0)

num_cols = bonemed_df %>% dplyr::select(where(is.numeric)) %>% colnames()
loess_plot = num_cols[c(-1, -2, -3, -9)]

@@

### Observations:
* The Loess plots show the 'age', 'height' and 'fracscore' have an  S curve like logistic model.

@@

## Manual selection
```{r, feature selection manual selection}
# Fit each variable separately and check the p-value for significance

# priorfrac
simple.log.priorfrac<-glm(fracture~priorfrac,family="binomial",data=bonemed_df)
simple.log.priorfrac.sum = summary(simple.log.priorfrac)

# age
simple.log.age<-glm(fracture~age,family="binomial",data=bonemed_df)
simple.log.age.sum = summary(simple.log.age)

# weight
simple.log.weight<-glm(fracture~weight,family="binomial",data=bonemed_df)
simple.log.weight.sum = summary(simple.log.weight)

# height
simple.log.height<-glm(fracture~height,family="binomial",data=bonemed_df)
simple.log.height.sum = summary(simple.log.height)

# bmi
simple.log.bmi<-glm(fracture~bmi,family="binomial",data=bonemed_df)
simple.log.bmi.sum = summary(simple.log.bmi)

# premeno
simple.log.premeno<-glm(fracture~premeno,family="binomial",data=bonemed_df)
simple.log.premeno.sum = summary(simple.log.premeno)

# momfrac
simple.log.momfrac<-glm(fracture~momfrac,family="binomial",data=bonemed_df)
simple.log.momfrac.sum = summary(simple.log.momfrac)

# armassist
simple.log.armassist<-glm(fracture~armassist,family="binomial",data=bonemed_df)
simple.log.armassist.sum = summary(simple.log.armassist)

# smoke
simple.log.smoke<-glm(fracture~smoke,family="binomial",data=bonemed_df)
simple.log.smoke.sum = summary(simple.log.smoke)

# raterisk
simple.log.raterisk<-glm(fracture~raterisk,family="binomial",data=bonemed_df)
simple.log.raterisk.sum = summary(simple.log.raterisk)

# fracscore
simple.log.fracscore<-glm(fracture~fracscore,family="binomial",data=bonemed_df)
simple.log.fracscore.sum = summary(simple.log.fracscore)

# bonemed
simple.log.bonemed<-glm(fracture~bonemed,family="binomial",data=bonemed_df)
simple.log.bonemed.sum = summary(simple.log.bonemed)

# bonemed_fu
simple.log.bonemed_fu<-glm(fracture~bonemed_fu,family="binomial",data=bonemed_df)
simple.log.bonemed_fu.sum = summary(simple.log.bonemed_fu)

# bonetreat
simple.log.bonetreat<-glm(fracture~bonetreat,family="binomial",data=bonemed_df)
simple.log.bonetreat.sum = summary(simple.log.bonetreat)
```

@@

### Observations:
* We can see that the following variables are statistically significant since p-value < 0.05:
 1. priorfracYes
 2. age
 3. height
 4. momfracYes
 5. armassistYes
 6. rateriskGreater
 7. fracscore
 8. bonemedYes
 9. bonemed_fuYes
 10. bonetreatYes

@@

```{r, all variables manual}
multi_var.log<-glm(fracture~priorfrac+age+weight+height+bmi+premeno+momfrac+armassist+smoke+raterisk+fracscore+bonemed+
                     bonemed_fu+bonetreat,family="binomial",data=bonemed_df)
multi_var.log.sum = summary(multi_var.log)
multi_var.log.sum$coefficients
```

@@

### Remove the multicollinearity
```{r, all variables manual wo multicollinearity}
multi_var.log.vif<-glm(fracture~priorfrac+age+weight+height+premeno+momfrac+armassist+smoke+raterisk+fracscore+bonemed+
                     bonemed_fu+bonetreat,family="binomial",data=bonemed_df)
multi_var.log.vif.sum = summary(multi_var.log.vif)
multi_var.log.vif.sum$coefficients

```

@@

```{r, stepwise}
bonemed_df.step = bonemed_df[,c('priorfrac', 'age', 'weight', 'height', 'bmi', 'premeno', 'momfrac', 'armassist', 'smoke', 'raterisk', 'fracscore', 
                                'bonemed', 'bonemed_fu', 'bonetreat', 'fracture')]
step.full.log = glm(fracture~.,family="binomial",data=bonemed_df.step)
step.log = step.full.log %>% stepAIC(trace=FALSE)
```

@@

## Obseravtions:
* Running a stepwise selection to identify the most important predictors the

#####################################################################################
#                                       Prediction                                  #
#####################################################################################
#####################################################################################
#                    Split the Data to Train and Test sets (85%-15%)               #
#####################################################################################
```{r train test set}
index<-sample(1:dim(bonemed_df)[1],round(dim(bonemed_df)[1]*0.85),replace=F)
train = bonemed_df[index,]
test = bonemed_df[-index,]
```

>>>>

# Other useful libraries
library(dplyr)
library(ggplot2)
library(gplots)

@@

#####################################################################################
#                                     Correlation plot                              #
#####################################################################################
```{r correlation plot}
corr_df = bonemed_df[,c('age', 'weight', 'height', 'bmi', 'fracscore')]
cont_var.cor = cor(corr_df)
heatmap.2(cont_var.cor,col=redgreen(75), 
          density.info="none", trace="none", dendrogram=c("row"), 
          symm=F,symkey=T,symbreaks=T, scale="none")
```

### Observations:
* weight and bmi are more similar to each other therefore they would form a cluster
* height, weight and bmi are also similar but more distant from each other. Still can form a cluster.
* age and fracscore are also similar to each other and can form a cluster

```{r}
# Label encoding Yes=1; No=0
bonemed_df$fracture.num<-ifelse(bonemed_df$fracture=="Yes",1,0)
```

#####################################################################################
#                                       Loess plots                                 #
#####################################################################################
```{r, Loess plot}
num_cols = bonemed_df %>% dplyr::select(where(is.numeric)) %>% colnames()
loess_plot = num_cols[c(-1, -2, -3, -9)]

@@

### Observations:
* The Loess plots show the 'height' has an  S curve like logistic model. The curve is trending down.
* The other continuous predictors don't seem to be important predicting fracture in the first year.

#####################################################################################
#                   Loess plots to investigate interactions                         #
#####################################################################################
```{r, Loess plot interaction}
num_cols = bonemed_df %>% dplyr::select(where(is.numeric)) %>% colnames()
loess_plot = num_cols[c(-1, -2, -3, -9)]

for (j in cat_cols)
{
  for (i in loess_plot)
  {
  plot1 = ggplot(bonemed_df,aes(x=.data[[i]],y=fracture.num,colour=.data[[j]]))+geom_point()+
  theme(plot.title = element_text(hjust = 0.5)) +
  ggtitle(paste(i, "&", j, " interaction with fracture"))+
  geom_smooth(formula = y ~ x, method="loess",size=1,span=1.5)+facet_wrap(~.data[[j]])
  ylim(-.2,1.2)
  show(plot1)
  }
}
```

## Observations:
* There is a interaction with weight and priorfrac
* There is a interaction with bmi and priorfrac
* There is a interaction with fracscore and priorfrac
* There is a interaction with weight and raterisk
* There is a interaction with bmi and raterisk
* There is a interaction with weight and bonemed
* There is a interaction with bmi and bonemed
* There is a interaction with weight and bonemed_fu
* There is a interaction with bmi and bonemed_fu
* There is a interaction with weight and bonetreat
* There is a interaction with bmi and bonetreat

#####################################################################################
#                    Split the Data to Train and Test sets (85%-15%)               #
#####################################################################################
```{r train test set}
bonmed_df_split = bonemed_df[,-c(1, 2, 3)]
index<-sample(1:dim(bonmed_df_split)[1],round(dim(bonmed_df_split)[1]*0.85),replace=F)
train = bonmed_df_split[index,]
test = bonmed_df_split[-index,]
```

@@

## Manual / Intuition selection
```{r, feature selection manual selection}
# Fit each variable separately and check the p-value for significance

# priorfrac
simple.log.priorfrac<-glm(fracture~priorfrac,family=binomial(link='logit'),data=train)
simple.log.priorfrac.sum = summary(simple.log.priorfrac)

# age
simple.log.age<-glm(fracture~age,family=binomial(link='logit'),data=train)
simple.log.age.sum = summary(simple.log.age)

# weight
simple.log.weight<-glm(fracture~weight,family=binomial(link='logit'),data=train)
simple.log.weight.sum = summary(simple.log.weight)

# height
simple.log.height<-glm(fracture~height,family=binomial(link='logit'),data=train)
simple.log.height.sum = summary(simple.log.height)

# bmi
simple.log.bmi<-glm(fracture~bmi,family=binomial(link='logit'),data=train)
simple.log.bmi.sum = summary(simple.log.bmi)

# premeno
simple.log.premeno<-glm(fracture~premeno,family=binomial(link='logit'),data=train)
simple.log.premeno.sum = summary(simple.log.premeno)

# momfrac
simple.log.momfrac<-glm(fracture~momfrac,family=binomial(link='logit'),data=train)
simple.log.momfrac.sum = summary(simple.log.momfrac)

# armassist
simple.log.armassist<-glm(fracture~armassist,family=binomial(link='logit'),data=train)
simple.log.armassist.sum = summary(simple.log.armassist)

# smoke
simple.log.smoke<-glm(fracture~smoke,family=binomial(link='logit'),data=train)
simple.log.smoke.sum = summary(simple.log.smoke)

# raterisk
simple.log.raterisk<-glm(fracture~raterisk,family=binomial(link='logit'),data=train)
simple.log.raterisk.sum = summary(simple.log.raterisk)

# fracscore
simple.log.fracscore<-glm(fracture~fracscore,family=binomial(link='logit'),data=train)
simple.log.fracscore.sum = summary(simple.log.fracscore)

# bonemed
simple.log.bonemed<-glm(fracture~bonemed,family=binomial(link='logit'),data=train)
simple.log.bonemed.sum = summary(simple.log.bonemed)

# bonemed_fu
simple.log.bonemed_fu<-glm(fracture~bonemed_fu,family=binomial(link='logit'),data=train)
simple.log.bonemed_fu.sum = summary(simple.log.bonemed_fu)

# bonetreat
simple.log.bonetreat<-glm(fracture~bonetreat,family=binomial(link='logit'),data=train)
simple.log.bonetreat.sum = summary(simple.log.bonetreat)
```

@@

### Observations:
* We can see that the following variables are statistically significant since p-value < 0.05:
 1. priorfracYes
 2. age
 3. height
 4. armassistYes
 5. rateriskSame
 6. rateriskGreater
 7. fracscore
 8. bonemedYes
 9. bonemed_fuYes
 10. bonetreatYes

@@

## Fit all variables at the same time to check effects 
```{r, all variables manual}
multi_var.log<-glm(fracture~priorfrac+age+weight+height+bmi+premeno+momfrac+armassist+smoke+raterisk+fracscore+bonemed+
                     bonemed_fu+bonetreat,family=binomial(link='logit'),data=train)
multi_var.log.sum = summary(multi_var.log)
multi_var.log.sum$coefficients
```

@@

### Remove the multicollinearity
```{r, all variables manual wo multicollinearity}
multi_var.log.vif<-glm(fracture~priorfrac+age+weight+height+premeno+momfrac+armassist+smoke+raterisk+fracscore+bonemed+
                     bonemed_fu+bonetreat,family=binomial(link='logit'),data=train)
multi_var.log.vif.sum = summary(multi_var.log.vif)
multi_var.log.vif.sum$coefficients
```

@@

```{r, stepwise}
bonemed_df.step = train[,c('priorfrac', 'age', 'weight', 'height', 'bmi', 'premeno', 'momfrac', 'armassist', 'smoke', 'raterisk', 'fracscore', 
                                'bonemed', 'bonemed_fu', 'bonetreat', 'fracture')]
step.full.log = glm(fracture~.,family=binomial(link='logit'),data=bonemed_df.step)
step.log = step.full.log %>% stepAIC(trace=FALSE)
```

@@

## Obseravtions:
* Running a stepwise selection to identify the predictors the process is selecting:
* priorfrac
* age
* weight
* bmi
* momfrac
* armassist
* raterisk
* bonemed
* bonemed_fu
* bonetreat

## PCA
```{r, PCA}
# Let's use PCA to see if the continuous variables separate or not

num_cols = train %>% dplyr::select(where(is.numeric)) %>% colnames()
pca_var = num_cols[c(-6)]
pca_df = train[pca_var]

pc.result=prcomp(pca_df,scale.=TRUE)
pc.scores=pc.result$x
pc.scores=data.frame(pc.scores)
pc.scores$fracture=train$fracture

#plot the first few pc's
ggplot(data = pc.scores, aes(x = PC1, y = PC2)) +
  geom_point(aes(col=fracture), size=1)+
  theme(plot.title = element_text(hjust = 0.5))+
  ggtitle("PC1 and PC2 on Fracture")

# Let's check lower PCs
ggplot(data = pc.scores, aes(x = PC1, y = PC3)) +
  geom_point(aes(col=fracture), size=1)+
  theme(plot.title = element_text(hjust = 0.5))+
  ggtitle("PC1 and PC3 on Fracture")

ggplot(data = pc.scores, aes(x = PC1, y = PC4)) +
  geom_point(aes(col=fracture), size=1)+
  theme(plot.title = element_text(hjust = 0.5))+
  ggtitle("PC1 and PC4 on Fracture")

ggplot(data = pc.scores, aes(x = PC1, y = PC5)) +
  geom_point(aes(col=fracture), size=1)+
  theme(plot.title = element_text(hjust = 0.5))+
  ggtitle("PC1 and PC5 on Fracture")

ggplot(data = pc.scores, aes(x = PC2, y = PC3)) +
  geom_point(aes(col=fracture), size=1)+
  theme(plot.title = element_text(hjust = 0.5))+
  ggtitle("PC2 and PC3 on Fracture")

ggplot(data = pc.scores, aes(x = PC2, y = PC4)) +
  geom_point(aes(col=fracture), size=1)+
  theme(plot.title = element_text(hjust = 0.5))+
  ggtitle("PC2 and PC4 on Fracture")

ggplot(data = pc.scores, aes(x = PC2, y = PC5)) +
  geom_point(aes(col=fracture), size=1)+
  theme(plot.title = element_text(hjust = 0.5))+
  ggtitle("PC2 and PC5 on Fracture")

ggplot(data = pc.scores, aes(x = PC3, y = PC4)) +
  geom_point(aes(col=fracture), size=1)+
  theme(plot.title = element_text(hjust = 0.5))+
  ggtitle("PC3 and PC4 on Fracture")

ggplot(data = pc.scores, aes(x = PC3, y = PC5)) +
  geom_point(aes(col=fracture), size=1)+
  theme(plot.title = element_text(hjust = 0.5))+
  ggtitle("PC3 and PC5 on Fracture")

ggplot(data = pc.scores, aes(x = PC4, y = PC5)) +
  geom_point(aes(col=fracture), size=1)+
  theme(plot.title = element_text(hjust = 0.5))+
  ggtitle("PC4 and PC5 on Fracture")

par(mfrow=c(1,2))
eigenvals = (pc.result$sdev)^2
plot(1:5,eigenvals/sum(eigenvals),type="l",main="Scree Plot",ylab="Prop. Var. Explained")
cumulative.prop = cumsum(eigenvals/sum(eigenvals))
plot(1:5,cumulative.prop,type="l",main="Cumulative proportion",ylim=c(0,1))
```

```{r, loess for PCI}
for (i in colnames(pc.scores))
{
loess_pca = pc.scores %>% 
ggplot(aes(x=.data[[i]],y=train$fracture.num))+
geom_point()+
geom_smooth(formula = y ~ x, method="loess")+
theme(plot.title = element_text(hjust = 0.5)) +
ggtitle(paste(i, " test"))
egg::ggarrange(loess_pca, ncol=2)
}
```

## Observations:
* The levels in the PCA graph are completely intermixed. There is no obvious separation in the PCA.
* The Scree Plot shows that if we include PC1 that will explain ~50% of the variation of the dataset
* The cumulative proportion plot helps us see that PC1, PC2, PC3 combined explains the variation ~98% but if we add PC4 than 100% of the variation is explained.
* This lets us conclude that we need 'age', 'weight', 'height' and 'bmi' to explain 100% of the variation in the data.
* The loess plot of PCA shows that PC3 is the only continous variable which could be important for predicting fracture in the first year.

## Penalized logistic regression (LASSO)
```{r, data prep for penalized logistic regression}
# Dummy code categorical predictor variables
x = model.matrix(fracture~., train)[,-c(1,17)]

# Convert the outcome (class) to a numerical variable
y <- train$fracture.num
```

```{r, lasso feature selection}
grid=10^seq(10,-2, length =100)
lasso.mod = glmnet(x, y, family = binomial(link='logit'), alpha=1, lambda=grid)
cv.out=cv.glmnet(x,y,family = "binomial", alpha=1)
plot(cv.out)

bestlambda = cv.out$lambda.min
coef(lasso.mod,s=bestlambda)

# Final LASSO model
lasso.mod.final=glmnet(x,y,family = binomial(link='logit'), alpha=1, type.measure = "class", lambda=bestlambda)
```

#####################################################################################
#                                       Predictions                                 #
#####################################################################################

```{r, vif function}
# VIF score function
vif_score = function(model_name)
{
  vif_values = vif(model_name)[,3]
  barplot(vif_values, main = 'VIF Values', horiz = TRUE, col="blue", xlim = c(0,12))
  abline(v=10, col="red")
  return (vif_values)
}
```

```{r, y.test}
y.test = model.matrix(fracture~., test)[,-c(1,17)]
```
#####################################################################################
#                                       LASSO                                       #
#####################################################################################
```{r, LASSO Predict}
cutoff.lasso<-0.43
# Predicting on the final LASSO model TRAINing data
lasso.mod.final.pred.train <- predict(lasso.mod.final, newx = x, type = "response")

# Confusion matrix
class.lasso.final.train<-factor(ifelse(lasso.mod.final.pred.train>cutoff.lasso,"Yes","No"),levels=c("No","Yes"))

#Confusion Matrix for LASSO
print("Confusion matrix for LASSO TRAINING with 0.5 cutoff")
confusionMatrix(table(class.lasso.final.train,train$fracture))

################ Misclassification rate train ######################################
#cross.table.lasso.train = table(table(class.lasso.final.train,train$fracture))
#MCR_lasso.train = (cross.table.lasso.train[2]+cross.table.lasso.train[3])/dim(train)[1]
misClasificError.lasso.train = mean(class.lasso.final.train != train$fracture)
print(paste('Misclassification Rate for lasso on training set: ', misClasificError.lasso.train))
#####################################################################################################
# Predicting on the final LASSO model TEST data
lasso.mod.final.pred.test <- predict(lasso.mod.final, newx = y.test, type = "response")

# Confusion matrix
class.lasso.final.test<-factor(ifelse(lasso.mod.final.pred.test>cutoff.lasso,"Yes","No"),levels=c("No","Yes"))

#Confusion Matrix for LASSO
print("Confusion matrix for LASSO TEST with 0.5 cutoff")
confusionMatrix(table(class.lasso.final.test,test$fracture))

################ Misclassification rate test ######################################
#cross.table.lasso.test = table(class.lasso.final.test,test$fracture)
#MCR_lasso.test = (cross.table.lasso.test[2]+cross.table.lasso.test[3])/dim(test)[1]
#print(paste('Misclassification Rate for LASSO selection on test set: ', MCR_lasso.test))
misClasificError.lasso.test = mean(class.lasso.final.test != test$fracture)
print(paste('Misclassification Rate for lasso on test set: ', misClasificError.lasso.test))

################ LASSO ROC Curve ######################################
library(ROCR)
lasso.roc.test = prediction(lasso.mod.final.pred.test, test$fracture,label.ordering=c("No","Yes"))
roc.lasso.test = performance(lasso.roc.test, measure = "tpr", x.measure = "fpr")
plot(roc.lasso.test,colorize = TRUE)
abline(a=0, b= 1)
```

## Assumprions
```{r, fit after feature selection2}
# Checking logistic regression model assumptions

# The Observations are Independent
# We can assume that the observations are not coming from repeated measures

#There is No Multicollinearity Among Explanatory Variables
### Visualize VIF
#vif_score(lasso.mod)

# There are No Extreme Outliers (cooks D)
#influenceIndexPlot(lasso.mod)

# There is a Linear Relationship Between Explanatory Variables and the Logit of the Response Variable

# Influential point analysis and residual plots
#residualPlots(lasso.mod)
#influenceIndexPlot(lasso.mod)
#influencePlot(lasso.mod)
```

## Observations:
## All assumptions are met:
* __The Response Variable is Binary__: 'Fracture' as a response variable is a factor with binary levels (Yes/No)
* __Independence__: We can assume that the observations are independent
* __Multicolliearity__: The is no multicollinearity among the explanatory variables (VIF values show no multicollinearity)
* __Outliers__: The largest Cooks D value is 0.015 which indicates that there is no extreme outlier
* __The Sample Size is Sufficiently Large__: ?

## Model scoring
```{r model scoring lasso}
## Add misclassification rate
```

#####################################################################################
#                                       Stepwise                                    #
#####################################################################################
```{r, Stepwise Predict}
cutoff.step = 0.42
# Predicting on the final Stepwise model TRAINing data
stepwise.mod.final.pred.train <- predict(step.log, newdata = train, type = "response")

# Confusion matrix
class.stepwise.final.train<-factor(ifelse(stepwise.mod.final.pred.train>cutoff.step,"Yes","No"),levels=c("No","Yes"))

#Confusion Matrix for Stepwise
print("Confusion matrix for Stepwise TRAINING with 0.5 cutoff")
confusionMatrix(table(class.stepwise.final.train,train$fracture))

################ Misclassification rate train ######################################
#cross.table.stepwise.train = table(class.stepwise.final.train,train$fracture)
#MCR_stepwise.train = (cross.table.stepwise.train[2]+cross.table.stepwise.train[3])/dim(train)[1]
#print(paste('Misclassification Rate for stepwise selection on training set: ', MCR_stepwise.train))

misClasificError.stepwise.train = mean(class.stepwise.final.train != train$fracture)
print(paste('Misclassification Rate for stepwise on train set: ', misClasificError.stepwise.train))

#####################################################################################################
# Predicting on the final Stepwise model TEST data
stepwise.mod.final.pred.test <- predict(step.log, newdata = test, type = "response")

# Confusion matrix
class.stepwise.final.test<-factor(ifelse(stepwise.mod.final.pred.test>cutoff.step,"Yes","No"),levels=c("No","Yes"))

#Confusion Matrix for Stepwise
print("Confusion matrix for Stepwise TEST with 0.5 cutoff")
confusionMatrix(table(class.stepwise.final.test,test$fracture))

################ Misclassification rate test ######################################
#cross.table.stepwise.test = table(class.stepwise.final.test,test$fracture)
#MCR_stepwise.test = (cross.table.stepwise.test[2]+cross.table.stepwise.test[3])/dim(test)[1]
#print(paste('Misclassification Rate for stepwise selection on test set: ', MCR_stepwise.test))

misClasificError.stepwise.test = mean(class.stepwise.final.test != test$fracture)
print(paste('Misclassification Rate for stepwise on test set: ', misClasificError.stepwise.test))

# ODD ratios for interpretation
summary(step.log)
exp(cbind("Odds ratio" = coef(step.log), confint.default(step.log, level = 0.95)))

################ Stepwise ROC Curve ######################################
library(ROCR)
stepwise.roc.test = prediction(stepwise.mod.final.pred.test, test$fracture,label.ordering=c("No","Yes"))
roc.stepwise.test = performance(stepwise.roc.test, measure = "tpr", x.measure = "fpr")
plot(roc.stepwise.test,colorize = TRUE)
abline(a=0, b= 1)
```

#####################################################################################
#                                       Manual/Intuition                            #
#####################################################################################

```{r, manual selection prediction}
# 5-fold cross validation
cv <- trainControl(
  method = "repeatedcv", 
  number = 5,
  repeats = 10,
  savePredictions = TRUE,
  summaryFunction=mnLogLoss,
  classProbs = TRUE
)

MLogReg = train(
  fracture ~ age + height + bmi + priorfrac,
  data = train,
  method = "glm",
  family = "binomial",
  trControl = cv,
  metric = "logLoss")

### Visualize VIF
MLogReg_VIF = vif(MLogReg$finalModel)
barplot(MLogReg_VIF, main = 'VIF Values (Custom Logistic Regression', horiz = TRUE, col="blue", xlim = c(0,12))
abline(v=10, col="red")

### Hypothesis testing
summary(MLogReg$finalModel)

anova(MLogReg$finalModel, test="Chisq")

library(ResourceSelection) 
hoslem.test(MLogReg$finalModel$y,fitted(MLogReg))

# Predicting
MLogReg.pred.train = predict(MLogReg, train)
MLogReg.pred.test = predict(MLogReg, test)

#Confusion Matrix for manual
confusionMatrix(table(MLogReg.pred.train,train$fracture))
confusionMatrix(table(MLogReg.pred.test,test$fracture))

################ Misclassification rate train ######################################
cross.table.manual.train = table(MLogReg.pred.train,train$fracture)
MCR_manual.train = (cross.table.manual.train[2]+cross.table.manual.train[3])/dim(train)[1]
print(paste('Misclassification Rate for manual selection on training set: ', MCR_manual.train))

################ Misclassification rate test ######################################
cross.table.manual.test = table(MLogReg.pred.test,test$fracture)
MCR_manual.test = (cross.table.manual.test[2]+cross.table.manual.test[3])/dim(test)[1]
print(paste('Misclassification Rate for manual selection on test set: ', MCR_manual.test))

################ Manual ROC Curve ######################################
#library(ROCR)
#manual.roc.test = prediction(as.numeric(MLogReg.pred.test), as.numeric(test$fracture), label.ordering=c("No","Yes"))
#roc.manual.test = performance(manual.roc.test, measure = "tpr", x.measure = "fpr")
#plot(roc.manual.test,colorize = TRUE)
#abline(a=0, b= 1)
```

#####################################################################################
#                                       Objective II                                #
#####################################################################################

```{r, interaction}
cutoff.manual = 0.5
LogReg.Interaction<-glm(fracture~age + height + bmi + priorfrac, family=binomial(link='logit'))
LogReg.Interaction.pred.train <- predict(LogReg.Interaction, newdata = train, type = "response")

Anova(LogReg.Interaction,type=3)

# Confusion matrix
class.LogReg.Interaction.train<-factor(ifelse(LogReg.Interaction.pred.train>cutoff.manual,"Yes","No"),levels=c("No","Yes"))

#Confusion Matrix for interaction
print("Confusion matrix for Interaction TRAINING with 0.5 cutoff")
confusionMatrix(table(class.LogReg.Interaction.train,train$fracture))

################ Misclassification rate train ######################################
cross.table.interaction.train = table(class.LogReg.Interaction.train,train$fracture)
MCR_interaction.train = (cross.table.interaction.train[2]+cross.table.interaction.train[3])/dim(train)[1]
print(paste('Misclassification Rate for stepwise selection on training set: ', MCR_interaction.train))
```
